Life course and long-term perspectives of social inequality in mortality among elderly and adults in Northern Sweden 1801--2013

### 2017-10-19 article3.Rmd
first commit (copy of 'article2.Rmd')

---
title: Life course and long-term perspectives of social inequality in mortality among
  elderly and adults in Northern Sweden      1801–2013
author: "S&ouml;ren Edvinsson and G&ouml;ran Brostr&ouml;m"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(engine='R',fig.path='figs/art2-',tidy=FALSE,fig.height=3.5,fig.width=8,strip.white=TRUE,cache=FALSE,echo=FALSE,message=FALSE,comment=NA,show.signif.stars = FALSE)##$
library(knitr)
library(eha)
library(xtable)
library(skum)
```

>>>>

---
title: Life course and long-term perspectives of social inequality in mortality among elderly and adults in Northern Sweden 1801--2013
author: "S&ouml;ren Edvinsson and G&ouml;ran Brostr&ouml;m"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(engine='R',fig.path='figs/art3-',tidy=FALSE,fig.height=3.5,fig.width=8,strip.white=TRUE,cache=FALSE,echo=FALSE,message=FALSE,comment=NA,show.signif.stars = FALSE)##$
library(knitr)
library(eha)
library(xtable)
library(skum)
```
